Deeply Virtual Compton Scattering measurement off bound protons

### 2018-10-10 eg6-letters/incoherent/incoherent_prl.tex
implement the corrections from Stepan

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the 
BSA can be simplified as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ 
and is proportional to the following combination of Compton form factors (CFF) 
\cite{Guidal:2013rya}
\begin{equation}
   a_{0} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} F_2 
   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors and $x_B$ the 
Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  
\begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi) \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, there $\xi$ is the 
skewing factor and can be
related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$. Similar expressions apply 
for the GPDs $E$, $\widetilde{H}$, and $\widetilde{E}$.

@@

In the kinematical phase-space of our experiment, the GPD $H$ is
expected to dominate the 
contribution in the BSA over the other three GPDs. There, 
the $\phi$ dependence of $A_{LU}$ is mostly sensitive to the  
imaginary part of the CFF $\mathcal{H}$ through the parameters $a_0$ of 
equation~\ref{eq:alu-simp}. The measurement of the free proton 
$A_{LU}$ \cite{Girod:2007aa} has confirmed that the $a_0$ term is 
dominating the shape of the distribution.

@@

FIG.~\ref{fig:alu90} presents the dependence of the fitted $A_{LU}$ values at 
$\phi$~=~90$^{\circ}$ ($a_{0}$ parameter from the individual fits in 
FIG.~\ref{fig:alu}) on the kinematical variables $Q^2$, $x_{B}$, and $t$.  
Within the given uncertainties, $A_{LU}$ does not indicate a strong dependence 
on $Q^2$.  The $x_{B}$ and $t$ dependency are compared to theoretical 
calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
model uses a nuclear spectral function and considers mainly off-shell effects.  
The calculations are carried out at slightly different kinematics than our data 
but still provide important guidance. The experimental results appear to have 
smaller asymmetries especially at low $x_{B}$ than the calculations. These 
differences may arise from nuclear effects which are not taken into account in 
the model, such as long-range interactions and final state interactions of the 
knock-out proton. On the graph for $-t$ dependence, we show previous 
measurements by the HERMES collaboration \cite{Airapetian:2009cga}, in which 
only electrons and photons were measured. Due to the large experimental 
uncertainties of the HERMES points, the two measurements are completely 
compatible.

>>>>

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the BSA can 
be parametrized as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ 
and is proportional to the following combination of Compton form factors (CFF) 
\cite{Guidal:2013rya}
\begin{equation}
   a_{0} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} F_2 
   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors, respectively, and 
$x_B$ the Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  \begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi) \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, there $\xi$ is the 
skewing factor and can be
related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$. Similar expressions apply 
for the GPDs $E$, $\widetilde{H}$, and $\widetilde{E}$.

@@

In the kinematical phase-space of our experiment, the GPD $H$ is
expected to dominate the contribution in the BSA over the other three GPDs.  
There, the $\phi$ dependence of $A_{LU}$ is mostly sensitive to the  imaginary 
part of the CFF $\mathcal{H}$ through the parameter $a_0$ of 
equation~\ref{eq:alu-simp}. The measurement of the free proton $A_{LU}$ 
\cite{Girod:2007aa} has confirmed that the $a_0$ term is dominating the shape 
of the distribution.

@@

FIG.~\ref{fig:alu90} presents the dependence of the fitted $A_{LU}$ values at 
$\phi$~=~90$^{\circ}$ ($a_{0}$ parameter from the individual fits in 
FIG.~\ref{fig:alu}) on the kinematical variables $Q^2$, $x_{B}$, and $t$.  
Within the given uncertainties, $A_{LU}$ does not indicate a strong dependence 
on $Q^2$.  The $x_{B}$ and $t$ dependencies are compared to theoretical 
calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
model uses a nuclear spectral function and considers mainly off-shell effects.  
The calculations are carried out at slightly different kinematics than our data 
but still provide important guidance. The experimental results appear to have 
smaller asymmetries especially at small $x_{B}$ than the calculations. These 
differences may arise from nuclear effects which are not taken into account in 
the model, such as long-range interactions and final state interactions of the 
knock-out proton. On the graph for $-t$ dependence, we show previous 
measurements by the HERMES collaboration \cite{Airapetian:2009cga}, in which 
only electrons and photons were measured. Due to the large experimental 
uncertainties of the HERMES points, the two measurements are completely 
compatible.
